Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-04-29 tex/paper1/paper1.tex
more refs and text

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jack.ireland@nasa.gov}

@@

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
regions considered.  It is clear that the Fourier power spectra
exhibit power-law like characteristics.

\begin{figure}
\label{fig:geom171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.geometric_mean_power_spectra.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
\caption{}
\end{figure}

\begin{figure}
\label{fig:geom193}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.geometric_mean_power_spectra.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.geometric_mean_power_spectra.eps}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbump}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

These two models are fit to the data (black solid lines, Figures
\ref{} and \ref{}). The

@@

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Coronal moss regions seem to show
slightly higher emission than a background power-law at a limited
range of frequencies.  However, this does not change the power-law
like nature of the emission - the power spectrum is essentially scale
free on average.  Therefore, on average, there is little guidance to
be had from coronal Fourier power spectra that can be used to pick a
time-scale that can be used to remove a background trend.

If there is no time-scale that can be used to remove a background
trend, then the time-series has to be analyzed without this processing
step.  Here too, the red-noise nature of the emission can cause
problems in attempting to analyze for the presence of narrow frequency
band oscillations.  Such oscillations are thought to be indicative of
waves in the solar atmosphere.

@@

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000} and looking for alternating brightening/darkening
in those plots as a indicator of a propagating wave.  This is
essentially a coherence-based approach, as the user is assessing the
likelihood that an oscillation has been detected based on the observed
signal in multiple contiguous pixels.  However, each pixel in these
plots probably has a red-noise background power spectrum, and so the
discussion of Section \ref{ssec:corseis} suggests that the
significance of any claimed oscillation is much reduced.

@@

It would be tempting to take this excess contribution and infer a
distribution of field line angles with the solar surface.  This
distribution relies on the assumption that all the
Gaussian-distributed component is entirely due to the channeling of
photospheric oscillatory power up to ``coronal'' heights and
temperatures.  However ??? has shown that moss has a relatively

@@

\section{Determining the number of independent
  measurements}\label{sec:app:ind}

>>>>

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jack.ireland@nasa.gov}
\newcommand{\Fps}{Fourier power spectrum}

@@

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.

\begin{figure}
\label{fig:fit171}
\plottwo{}{}
\plottwo{}{}
\caption{}
\end{figure}

\begin{figure}
\label{fig:fit193}
\plottwo{}{}
\plottwo{}{}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model for these regions
should be considered.  The spectrum $P_{1}$ where
\begin{equation}
\label{eq:pwrlawbump}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
each model to the data (for details on the fitting procedure, see
Section \ref{sec:app:ind}).

@@

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the Gaussian contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and Gaussian
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

The presence of a non-power law contribution to the \Fps\ does not
change the fact that the background emission is essentially power-law
like.  For the frequencies that have been of interest in coronal
seismology, the background power spectrum is therefore scale free on
average.  If there is no time-scale that can be used to remove a
background trend, then the time-series has to be analyzed without this
processing step.  A lack of awareness of the background red-noise
nature of the emission can cause problems in attempting to analyze for
the presence of narrow frequency band oscillations, as the following
example demonstrates.

@@

This has been recognized by \cite{2010MNRAS.402..307V} in the study of
XMM-Newton observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model comparison and fitting
technique that can be used to determine the presence of a narrow-band
features in Fourier power spectra against a red-noise like background
emission.  This technique is applicable to the search for oscillatory
power in coronal time-series.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000, 2003A&A...404L...1K} and looking for alternating
brightening/darkening in those plots as a indicator of a propagating
wave.  This is essentially a coherence-based approach, as the user is
assessing the likelihood that an oscillation has been detected based
on the observed signal in multiple contiguous pixels.  However, each
pixel in these plots probably has a red-noise background power
spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
that the significance of any claimed oscillation is much reduced.

@@

It would be tempting to take this excess contribution and infer a
distribution of field line angles with the solar surface.  This
distribution relies on the assumption that all the
Gaussian-distributed component is entirely due to the channeling of
photospheric oscillatory power up to ``coronal'' heights and
temperatures.

@@

\section{Model fitting procedure}\label{sec:app:ind}
